Impact ionization processes in a photodriven Mott insulator: influence of phononic dissipation

### 2022-11-07 resub_PRB/letters/reply_to_referees_current.txt

1. It is really important to discuss why DMFT approximation is
expected to be meaningful in quasi-2D case (1-layer Hubbard model
coupled to leads).

A1: As the Referee says, the system considered here is not strictly 2D. There is a coupling in the third direction due to the hybridization to the leads. Although these are noninteracting, they introduce a dissipation which suppresses 2D-coherence and makes nonlocal correlations less relevant.

On the other hand, it is true that antiferromagnetic (even short-range) correlations may play an important role in the spreading of photoexcited carriers, as discussed in Phys. Rev. Lett. 113, 076405
(2014). These nonlocal effects are not taken into account in our paper and certainly deserve future investigations.

As asked, we added in Sec. V a discussion on this point, with a reference to the paper mentioned above and to a comprehensive review of nonlocal correlations beyond DMFT [Rev. Mod. Phys. 90, 025003 (2018)].

### 2022-11-07 resub_PRB/Paper1.tex
typos fixing
Final version resubmitted to PRB

\begin{figure}[b] 
\includegraphics[width=0.75\linewidth]{Fig1.pdf}
\caption{(Color online) Schematic representation of the setup. A central, correlated layer with local Hubbard interaction $U$ and e-ph coupling $g$ (green) is sandwiched between two non-interacting layers (red) via the hybridization $v$ (black). The latter are in turn coupled to wide-band fermion reservoirs (blue) with different chemical potentials $\mu_{\text{l}/\text{r}}$, which introduce broadenings $\Gamma_{\text{l}/\text{r}}$.}
\label{fig:setup}
\end{figure}

@@

In order to study II in a Mott insulating layer, we adjust the bands to achieve the energy scheme shown in Fig.~\ref{fig:energy_setup}(a). We follow Ref.~\cite{so.do.18} and take $U=12$ and unless stated otherwise $E_0=2$. The fermion leads and the acoustic phonons have temperature $T=0.02$~\footnote{\resub{The value chosen for the temperature is much smaller as compared with the other characteristic energy scales of the system, e.g. $\omega_{\text{ph}}$, $U$ and $W_{\text{b}}$.}}. We consider a particle-hole symmetric system with $\Gamma_{\text{l}}=\Gamma_{\text{r}}=0.37$, $t_{\text{l}}=t_{\text{r}}=1.7$, $\varepsilon_{\text{l}/\text{r}}=\mp 6$ and $v_{\text{l}}=v_{\text{r}}=v$. The parameters $t_{\text{l/r}}$, $\varepsilon_{\text{l/r}}$, and  $\Gamma_{\text{l/r}}$ are chosen such that the leads' DOS approximately overlaps with the Hubbard bands, i.e. they exhibit a \textquoteleft bandwidth\textquoteright~\footnote{Notice that the support of the leads' spectra are formally infinite. $W_{\text{b}}$ is the value at which the spectrum gets  suppressed.} $W_{\text{b}}\approx 8$ and are centered at the same position. The chemical potentials are set to $\mu_{\text{l}/\text{r}} =\mp 1$, so that a current from left to right is produced by taking energy from the driving. Due to the hybridization with the leads, the local DOS of the Hubbard layer only features a pseudogap
 $\Delta_{\text{pg}} \approx 4$. All simulations are carried out with the dimensionless factor $\alpha\equiv t_{\text{resc}}E_0/\Omega^{2}<0.5$ for which the FDSA is justified~\footnote{In Ref.~\cite{so.do.18} the factor is defined as $\alpha=t_{c}E_0/\Omega^{2}$ and $t_{\text{c}}=1$. Setting $t_{\text{resc}}=1$, we define for consistency $\alpha$ as in the main text.}. Whenever the electron-phonon interaction is included, we take $g=0.8$ and unless stated otherwise $\omega_{\text{ph}}=0.1$.

@@

\resub{One should comment on the validity of DMFT, which should be accurate for large dimensions only, for the present quasi 2-D setup. As a matter of fact, the hybridization to the leads introduces a dissipation that suppresses 2D-coherence and thus makes nonlocal correlations beyond DMFT less relevant.
On the other hand, it has been shown that antiferromagnetic (even short-range) correlations may play an important role in the spreading of photoexcited carriers~\cite{ec.we.14}. 
Thaking into account the effect of such nonlocal correlations (see also ~\cite{ro.ha.18}) could be an interesting extension, although beyond the scope of the present research.}

@@

We thank A. Picano and C. Heil for fruitful discussions. This work was supported by the Austrian Science Fund (Grant No. P 33165-N) and by NaWi Graz. The computational results presented have been obtained using the Vienna Scientific Cluster (VSC) and the D-Cluster Graz.

>>>>

\begin{figure}[b] 
\includegraphics[width=0.8\linewidth]{Fig1.pdf}
\caption{(Color online) Schematic representation of the setup. A central, correlated layer with local Hubbard interaction $U$ and e-ph coupling $g$ (green) is sandwiched between two non-interacting layers (red) via the hybridization $v$ (black). The latter are in turn coupled to wide-band fermion reservoirs (blue) with different chemical potentials $\mu_{\text{l}/\text{r}}$, which introduce broadenings $\Gamma_{\text{l}/\text{r}}$.}
\label{fig:setup}
\end{figure}

@@

In order to study II in a Mott insulating layer, we adjust the bands to achieve the energy scheme shown in Fig.~\ref{fig:energy_setup}(a). We follow Ref.~\cite{so.do.18} and take $U=12$ and unless stated otherwise $E_0=2$. The fermion leads and the acoustic phonons have temperature $T=0.02$~\footnote{\resub{The value chosen for the temperature is much smaller than the other characteristic energy scales of the system, e.g. $\omega_{\text{ph}}$, $U$ and $W_{\text{b}}$.}}. We consider a particle-hole symmetric system with $\Gamma_{\text{l}}=\Gamma_{\text{r}}=0.37$, $t_{\text{l}}=t_{\text{r}}=1.7$, $\varepsilon_{\text{l}/\text{r}}=\mp 6$ and $v_{\text{l}}=v_{\text{r}}=v$. The parameters $t_{\text{l/r}}$, $\varepsilon_{\text{l/r}}$, and  $\Gamma_{\text{l/r}}$ are chosen such that the leads' DOS approximately overlaps with the Hubbard bands, i.e. they exhibit a \textquoteleft bandwidth\textquoteright~\footnote{Notice that the support of the leads' spectra are formally infinite. $W_{\text{b}}$ is the value at which the spectrum gets  suppressed.} $W_{\text{b}}\approx 8$ and are centered at the same position. The chemical potentials are set to $\mu_{\text{l}/\text{r}} =\mp 1$, so that a current from left to right is produced by taking energy from the driving. Due to the hybridization with the leads, the local DOS of the Hubbard layer only features a pseudogap
 $\Delta_{\text{pg}} \approx 4$. All simulations are carried out with the dimensionless factor $\alpha\equiv t_{\text{resc}}E_0/\Omega^{2}<0.5$ for which the FDSA is justified~\footnote{In Ref.~\cite{so.do.18} the factor is defined as $\alpha=t_{c}E_0/\Omega^{2}$ and $t_{\text{c}}=1$. Setting $t_{\text{resc}}=1$, we define for consistency $\alpha$ as in the main text.}. Whenever the electron-phonon interaction is included, we take $g=0.8$ and unless stated otherwise $\omega_{\text{ph}}=0.1$.

@@

\resub{One should comment on the validity of DMFT, which should be accurate for large dimensions only, for the present quasi two-dimensional (2D) setup. As a matter of fact, the hybridization to the leads introduces a dissipation which suppresses 2D-coherence and thus makes nonlocal correlations beyond DMFT less relevant.
On the other hand, it has been shown that antiferromagnetic (even short-range) correlations may play an important role in the spreading of photoexcited carriers~\cite{ec.we.14}. 
Taking into account the effect of such nonlocal correlations (see also~\cite{ro.ha.18}) might be an interesting extension, although beyond the scope of the present research.}

@@

We thank A. Picano \resub{and C. Heil} for fruitful discussions. This work was supported by the Austrian Science Fund \resub{(Grant No. P 33165-N) and by} NaWi Graz. The computational results presented have been obtained using the Vienna Scientific Cluster (VSC) and the D-Cluster Graz.
